Computer Science House Constitution

### 2024-02-20 constitution.tex
Removed extra newline that caused document to fail to compile (#151)
Clarify voting member of E-Board (#150)
Reordered dues table from most to least budget (#131)
Move Open House responsibilities to PR (#149)

% ARTICLE V - EXECUTIVE BOARD
\article{E-Board}
The E-Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.

\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House

@@

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evals Meetings
	\item To exercise general supervision over Evals operations
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
	\item To oversee the Membership Evals of Active Members
	\item To collaborate with the ResLife Advisor to determine room change selection and any changes of membership residency
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
	\item To prepare the House for Open Houses, tours, and special events
	\item To vote on issues presented to the Executive Board
\end{enumerate}

@@

\asubsection{Responsibilities of the PR Director}
\begin{enumerate}
	\item To preside over PR Directorship Meetings
	\item To operate House social media accounts intended to represent House as a whole
	\item To oversee the organization, initiation, and execution of House philanthropic events
	\item To preserve and improve the public image of House
	\item To collaborate with other E-Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
	\item To vote on issues presented to E-Board
\end{enumerate}

@@

\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
OpComm & 20\% \\
\hline
Evals & 5\% \\
\hline
History & 10\% \\
\hline
IMPs & 15\% \\
\hline
R\&D & 20\% \\
\hline
Social & 20\% \\
\hline
PR & 5\% \\
\hline
Accumulated & 5\% \\
\hline
\end{tabular}
\end{center}

>>>>

% ARTICLE V - EXECUTIVE BOARD
\article{E-Board}
The E-Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
A voting E-Board member is considered to be any person with a non-zero vote on E-Board. % Defined this way so that (for example) each member in a dual directorship is each considered to be a voting member on E-Board.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House.

@@

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evals Meetings
	\item To exercise general supervision over Evals operations
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
	\item To oversee the Membership Evals of Active Members
	\item To collaborate with the ResLife Advisor to determine room change selection and any changes of membership residency
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
	\item To vote on issues presented to the Executive Board
\end{enumerate}

@@

\asubsection{Responsibilities of the PR Director}
\begin{enumerate}
	\item To preside over PR Directorship Meetings
	\item To operate House social media accounts intended to represent House as a whole
	\item To oversee the organization, initiation, and execution of House philanthropic events
	\item To preserve and improve the public image of House
	\item To collaborate with other E-Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
    \item To oversee the preparation of House for Open Houses, tours, and special events
	\item To vote on issues presented to E-Board
\end{enumerate}

@@

\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
OpComm & 20\% \\
\hline
R\&D & 20\% \\
\hline
Social & 20\% \\
\hline
IMPs & 15\% \\
\hline
History & 10\% \\
\hline
Evaluations & 5\% \\
\hline
PR & 5\% \\
\hline
Accumulated & 5\% \\
\hline
\end{tabular}
\end{center}
